---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# databand

<!-- badges: start -->
<!-- badges: end -->

The aim of databand is to generate tables specifically for Excel export. A special feature is that the labels of variables are shown in the tables. The output is given in a list which can be exported to Excel. 

## Installation

You can install the development version of databand from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("mamayerl/databand")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(databand)
## basic example code
```

## Version and Changlog

0.1.0 Development Version: Setting up basic functions

## Known Bugs

- mean_bi: drop empty factor which shouldn't be
